---
title: "Simple document"
output: 
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
    pdf_document: default
    github_document: default

author: James Dalgleish
date: Sept 11, 2018

---
```{r setup, include = FALSE}
#all packages loaded here
library(tidyverse)
library(lme4)
library(MASS)
```

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r sample_chunk}
samp = rnorm(100)
length(samp)
```
This code chunk that creates a variable containing a sample of size 500 from a random normal variable, computes the absolute value of each element, and produces a histogram of the result. Add an inline summary giving the median value rounded to two decimal places.
```{r sample_500_hist}
hist(round(abs(rnorm(500)), digits = 2))
norm_500_abs_round<-as.data.frame(round(abs(rnorm(500)), digits = 2))
colnames(norm_500_abs_round)<-"sample_vals"
ggplot2::ggplot(norm_500_abs_round,ggplot2::aes(x=sample_vals)) + ggplot2::geom_histogram()
```

# Section 2
I can take the mean of the sample, too!
The mean is `r mean(samp)`.
#Section 3
Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell